Nengo: A Python tool for building large-scale functional brain models

### 2013-09-24 nengo.tex
Started implementing Aaron's suggestions

@@

Ideally, the entire state of a simulation
would be recorded on each timestep,
and stored with no overhead to the simulator.
In practice, recording data
is a costly part of most simulations,
and often what is simulated must also change
if the signals being probed must be filtered.
For this reason, probes are also
a core component of a Nengo model.

In general, Nengo objects and connections
each have several signals that can be probed.
For example, an ensemble's decoded value,
or the underlying neurons' membrane voltages
can be probed, among other signals.
The underlying logic for the probe
leverages connection logic,
making it easy to probe any part of an object.

@@

Once a model has been fully defined,
a simulator can be created to
run that model.
Simulators can be created
that work directly with the
objects described in section \ref{sec:objects}.
However, in the simulators that we have implemented
as reference, the model goes through a
two-stage build process in order to
simulate models as fast as possible.
In the first stage,
the model is ``built;''
i.e., the objects in the model are mapped to a simpler
set of objects that represent the computations
that the simulator must perform.
Those computations are analyzed in order to
schedule them efficiently.
In the second stage,
the simulator performs the computations
that have been scheduled on each timestep.

>>>>

However, the ability to connect neurons together
with synaptic connection weights is still possible
with the \texttt{NonlinearityConnection}.
Both of these connection types
can be temporally filtered,
and the weights involved in the connection
(decoding weights for \texttt{DecodedConnection},
synaptic connection weights for \texttt{NonlinearityConnection})
can be modified over time with learning rules.

@@

A probe is used to denotes a signal that
whose state will be recorded
throughout the simulation.
Nengo objects and connections
each have several signals that can be probed.
For an ensemble's decoded value,
or the underlying neurons' membrane voltages
can be probed, among others.

Ideally, the entire state of a simulation
would be recorded on each timestep,
and stored with no overhead to the simulator.
However, in practice, recording data
is a costly part of most simulations,
and often what is simulated must also change
if the signals being probed must be filtered.
For this reason, probes are also
a core component of a Nengo model.

@@

Once a model has been fully defined,
a simulator can be created to
run that model.
Simulators can be created
that work directly with the
objects described in section \ref{sec:objects}.
However, in the simulators that we have implemented
as reference, the model goes through a
two-stage process in order to
simulate models as fast as possible.
In the first stage,
the model is ``built;''
i.e., the objects in the model are mapped to a simpler
set of objects that represent the computations
that the simulator must perform.
Those computations are analyzed in order to
schedule them efficiently.
In the second stage,
the simulator performs the computations
that have been scheduled on each timestep.
